Contention Management for 5G

### 2017-05-19 article/article.tex
Reprise de l'intro

\maketitle
\begin{abstract}
This article treats about Contention Management for 5G.
\end{abstract}
The evolutions proposed in next generations of mobile network architectures aim at evolving toward centralized radio network architectures (C-RAN, for Cloud Radio Access Network) to reduce consumption costs and power at the base stations \cite{mobile2011c}. This type of architecture faces the challenge of mastering the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud. Low latency is already critical for the deployment of C-RAN approach. The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in less than from 1 to 10ms \cite{bouguen2012lte}
(depending on targeted services). One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU (this HARQ constraints must be enforced for each frame emitted every millisecond).\\
 Thus in this article, we work on latency and periodicity constraints in fronthaul.  The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.  It is then needed to find a solution to offer low latency over commoditized packet based networks. Indeed,  dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN. This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer). These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
 Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers. One of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
 statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
 Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}. To make DN working over a
 network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes. The major difficulty of this problem is the periodicity of the process. Indeed, a deterministic sending for the messages
between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
and following periods.\\

Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each destination node a route from one source node to it and a periodic routing scheme allowing to periodically sent a packet to each base station without congestion conflicts between all such packets and to insure a minimum latency. In a slotted time model, the aim is here to minimize the duration of the period, with a constraint of the maximum length of routes to be
selected. Even if the selected set of routes is given this optimization problem has been shown to be  \NP-hard. From an algorithmic point of view,
the purpose of this project is first, to study the complexity and the approximability of this problem when the length of the routes is small
(which corresponds to realistic cases), and secondly, to propose and implement some heuristics to solve this problem on realistic topologies.\\

@@

>>>>

\maketitle
\begin{abstract}
We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antenna and their computing unit located in distant data-centers.  We want to send the messages so that there are no congestion while minimizing the latency. We prove the problem is $\NP$-complete even when the graph is very simple. We then deal with the case of a star graph and for different regime of the parameters we propose several algorithms that are experimentally shown to work extremely well.
\end{abstract}

Next generations of mobile network architectures evolves toward centralized radio network architectures or C-RAN, for Cloud Radio Access Network, to reduce consumption costs and power at the base stations \cite{mobile2011c}. The main challenge for this type of architecture is the latency in the transfer process between the Remote Radio Heads (RRHs) on the field and baseband units (BBUs) in the cloud. The standard requires meeting time constraints for functions like HARQ (Hybrid Automatic Repeat reQuest) that needs to be processed in 1 to 10ms depending on targeted services~\cite{bouguen2012lte}. One specificity in the C-RAN context is not only the latency constraint, but also the periodicity of the data transfer between RRH and BBU.

 In this article, we study mechanisms to deal with the latency and periodicity constraints in fronthaul.  The current solution is to use statistical multiplexing with a traditional queue management and use an optical network with a very large bandwidth to minimize latency. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic
 Networking is under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}.

 We must manage the time at which the packets of each paths are sent, and we can introduce a deterministic waiting time in the BBU before the packet is sent back to the RRH. The aim is to avoid any collision in the vertices of the graph, which allows to avoid buffering and to guarantee the latency. 
  One major difficulty of this problem is the periodicity of the process. Indeed, a deterministic sending for the messages between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous and following periods.\\

%  to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches \cite{5gppparchitecture}. This architecture is very expensive and hardly scales in the case of a mobile network composed of about 10,000 base stations.  It is then needed to find a solution to offer low latency over commoditized packet based networks. Indeed,  dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN. This project proposes a new type of switching/routing node and a specific network architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer). These packets having a fixed duration close to $1\mu $s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.\\
%  Thus, new scheduling and routing paradigms and new technologies have to be considered to  guarantee  delay constrained periodic data transfers. One of the most promising approaches relies on the concept of Deterministic Networking (DN) such that one get rid of
%  statistical multiplexing. The traditional queue managements are replaced by time based forwarding. Solutions for Deterministic
%  Networking are under standardization in IEEE 802.1 TSN group \cite{finn-detnet-architecture-08}, as well at IETF DetNet working group \cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example \cite{howe2005time,leclerc2016transmission}. To make DN working over a
%  network composed of several nodes, it is required to manage the time at which the packets of deterministic paths are crossing each nodes. The major difficulty of this problem is the periodicity of the process. Indeed, a deterministic sending for the messages
% between each pair BBU/RRH must not collide with the other messages sent by the others BBU/RRH in the same period, but also in the previous
% and following periods.\\

Considering a graph, modeling the network topology, and a set of routes from source nodes (modeling connections to the BBU) and destination nodes (modeling the RRH) in this graph, the purpose is to select, for each route from one source node to its destination a periodic routing scheme. It must ensure that there are no congestion conflicts between packets and guarantee a minimum latency. The time will be discretized and a unit of time corresponds to the transmission of a minimal unit of data over the network.

@@

       Idée de David: deviner qu'est-ce qui coince, c'est à dire les routes qui ont une attente de 0, 
       ça donne des intervalles collés.
       Sinon on doit pouvoir faire du integer programming car le système est petit.
